\documentclass[a5paper,12pt]{memoir}
\usepackage{libertine}

\title{Prayers of St Gertrude for the Holy Souls}
\author{Preces Gertrudianae}


\begin{document}

\maketitle

\section{Offering of the Passion of Christ for the Faithful Departed.}

LOOK down, O Father of compassion, from thy high and 
holy seat upon the hapless souls detained in 
purgatory. Look upon all the pains and torments wherewith they 
are so piteously chastised; regard now the 
piteous groans and 
tears which they pour 
forth unto thee; hear 
the prayers and the 
supplications wherewith they entreat thy 
mercy, and be merciful unto their sins. Remember, O most compassionate Father, all 
the sufferings which 
thy Son hath endured 
for them; remember 
his Precious Blood, shed 
in such abundance 
for them; call to mind 
the most bitter death 
which he suffered for 
them, and have mercy on them. For all 
the sins they have ever committed against 
thee I offer thee the 
most holy life and conversation of thy most 
beloved Son; for all 
their negligences I offer thee his most fervent desires towards 
thee; for all their 
omissions I offer thee 
the great abundance 
of his merits; for their 
every insult and wrong 
to thee I offer thee 
the sweet submission 
with which he honoured thee. Finally, 
for all the chastisements which they have 
ever incurred I offer 
thee all the mortifications, fastings, watchings, the labours and 
afflictions, wounds and 
stripes, passion and 
death, which he endured in such spotless innocence and 
with such loving eagerness; beseeching 
thee now to suffer thy 
anger to be appeased 
towards them, and to 
lead them forth into 
everlasting joy. Amen. 

\section{Short and Efficacious Prayer for the Faithful Departed.}

O MOST compassionate Jesus, 
have mercy on the 
souls detained in purgatory, for whose redemption thou didst 
take upon thee our 
nature and endure a 
bitter death. Mercifully hear their groanings, look with pity 
on the tears which 
they now shed before 
thee, and by the virtue of thy Passion release them from the 
pains due unto their 
sins. O most pitiful 
Jesus, let thy precious 
Blood reach down into purgatory, and refresh and revive the 
captive souls which 
suffer there. Stretch forth unto them thy 
strong right hand, 
and bring them forth 
into the place of refreshment, light, and 
peace. Amen. 


\section{Four Prayers for the Departed.} 

Written by St. Gertrude with the approval 
of our Lord. 

\emph{When St. Gertrude 
was about to say these 
prayers together with the 
psalter, she asked our 
Lord whether they were 
acceptable to him, and 
received this answer : 
They are so acceptable 
to me that whenever a 
soul is liberated from 
purgatory, it is to me as 
though my own soul 
were delivered out of 
captivity, and I will 
surely reward them in 
due time, in the omnipotence of my boundless compassion. Wherefore, although you cannot recite the whole psalter, say at least these 
four most effectual prayers, and after each of 
them say :} 

HAIL, Jesus Christ, 
Splendour of the 
Father; hail, Prince of 
peace, Gate of heaven, 
living Bread, Offspring 
of the Virgin, Vessel 
of the Godhead. 

V. Eternal rest 
grant unto them, O 
Lord. 

R. And let perpetual light shine upon 
them. 

\emph{Or,} De profundis. 

\subsection{First Prayer.} 

I ADORE, salute, and 
bless thee, O sweetest Lord Jesus Christ, 
and I praise thee and 
give thee thanks with 
the love of all thy creatures for the vast love 
wherewith thou didst 
condescend to be made 
man for us, to be born , 
to endure hunger and 
thirst, toils and sorrows, for thirty-three 
years, and to bestow 
on us Thyself in the 
most holy Sacrament; 
beseeching thee that 
thou wouldst vouchsafe to unite and blend 
with the merits of thy 
most holy conversation and life this my 
prayer, which I make 
to thee for the soul of 
N. departed [or, for 
the souls of all the 
faithful departed]; 
and to supply from 
the great abundance 
of those merits, and 
perfectly to complete 
whatsoever he has neglected in thy worship 
and love, in thanksgiving and in prayer, 
in virtue and good 
works, and all the service due to thee, in all 
that by thy grace he 
might have done and 
has not done, or did 
from impure motives, 
or carelessly and imperfectly. Amen. 

\subsection{Second Prayer.} 

I ADORE, salute, and 
bless thee, O sweetest Lord Jesus Christ, 
and I give thee thanks 
for that love wherewith thou, the Creator 
of all things, didst 
condescend for our 
redemption to be seized and bound and 
dragged away to judgment, to be trampled 
upon, buffeted and 
spit upon, to be scourged and crowned with 
thorns, to be condemned, to bear thine own 
cross, to be stripped 
and nailed to the cross, 
to die a most bitter 
death, and to be pierced through with the 
lance. And in union 
with that love I offer 
thee these my unworthy prayers, beseeching thee to blot out and 
efface utterly through 
the merits of thy most 
holy Passion and Death 
whatsoever this soul 
for which I pray has 
ever done against thy 
will, by evil thoughts 
or words or deeds; 
and that thou wouldst 
vouchsafe to offer to 
God the Father all the 
sorrow and the anguish of thy torn Body 
and of thy desolated 
Soul, all thy merits 
and all thine actions, 
for all that chastisement which he has incurred at the hands of 
thy justice. Amen. 

\subsection{Third Prayer.}

I ADORE, salute, and 
bless thee, O sweetest Lord Jesus Christ, 
and I give thee thanks 
for all the love and 
the faithfulness with 
which thou didst overcome death and rise 
from the dead, and 
glorify our flesh by 
ascending in it to the 
right hand of the Father; beseeching thee 
that thou wouldst now 
vouchsafe to render 
the soul for which I 
pray partaker of thy 
triumph and of thy 
glory. Amen. 

\subsection{Fourth Prayer.}

I ADORE, salute, 
and bless thee, O 
sweetest Lord Jesus 
Christ, and I render 
thee thanks for all 
the graces thou hast 
ever bestowed on thy 
glorious Mother and 
on all thine elect, in 
union with the gratitude with which all 
thy saints exult in the 
bliss thou hast obtained for them through 
thy holy Incarnation, 
Passion, and Resurrection; beseeching 
thee that thou wouldst 
vouchsafe to supply 
to this soul from the 
merits and prayers of 
the same glorious Virgin and all thy saints, 
whatever is lacking to 
his own. Amen. 


\section{The Lord's Prayer for the Departed.}

\emph{On one occasion when 
St. Mechtilde had received holy Communion 
for the departed, our 
Lord appeared to her, 
saying: Recite for them 
one \emph{Our Father}. And 
as she prayed she received by divine inpiration the prayer which 
follows, the which when 
she had recited she saw 
a great multitude of 
souls ascending into 
heaven.} 

\emph{OUR Father, who art in heaven.} I 
beseech thee that 
thou wouldst forgive 
all the souls in purgatory, whereinsoever 
they have neither loved 
nor worthily honoured thee, their adorable 
and most beloved Father, who of thine 
own mere grace didst 
adopt them to be thy 
children, and have 
thrust thee forth from 
their hearts in which 
thou didst delight to 
dwell. And in satisfaction for this their 
sin, I offer thee that 
love and honour which 
thy beloved Son showed thee upon earth, 
and that most abundant satisfaction which 
he hath made for all 
their sins. Amen. 

\emph{Hallowed be thy 
Name.} I beseech 
thee, O thou Father 
of compassion, forgive 
the souls of the faithful departed whereinsoever they have not 
worthily honoured nor 
duly made mention of 
thy holy Name, but 
have taken it in vain, 
and by their scandalous life rendered 
themselves unworthy 
of the name of Christians. And in satisfaction for these their 
sins I offer thee the 
consummate holiness 
of thy Son, whereby he 
magnified thy Name 
by his teaching, and 
made it honourable by 
his work. Amen. 

\emph{Thy kingdom come.}
I beseech thee, O Father of compassion, 
vouchsafe to forgive 
the souls of the faithful departed whereinsoever they have not 
fervently longed nor 
ardently striven after 
thee and thy kingdom, in which alone 
is true rest and abiding glory. And for 
this and all their sloth 
in doing good I offer 
thee the most holy 
and longing desires 
of thy Son, wherewith 
he desired to make 
them heirs together 
with him of his kingdom. Amen. 

\emph{Thy will be done on 
earth as it is in heaven.} I beseech thee, 
O Father of compassion, vouchsafe to forgive the souls of the 
faithful departed, and 
especially of those 
consecrated to thee 
in the religious life, 
whereinsoever they 
have not preferred thy 
will above their own, 
nor have loved it in 
all things, but have 
too often lived and 
done only according to 
their own will. And 
in satisfaction for this 
their disobedience I 
offer thee the union 
of the sweetest Heart 
of thy Son with thy 
Will, and all that his 
most ready and loving obedience wherewith he was obedient 
unto thee, even to the 
death of the cross. 
Amen. 

\emph{Give us this day 
onr daily bread.} I 
beseech thee, O Father of compassion, 
vouchsafe to forgive 
the souls of the faithful departed whereinsoever they have not 
received the most 
blessed and adorable 
Sacrament of the Altar with pure and perfect desire, devotion, 
and love; or have received it unworthily, 
or seldom, or not at 
all. And in satisfaction for these their sins 
I offer thee the consummate holiness and 
the devotion of thy 
Son, together with 
that most ardent love 
and ineffable yearning desire wherewith 
he bestowed upon us 
this most inestimable 
treasure. Amen. 

\emph{And forgive us our 
trespasses, as we forgive them that trespass 
against us.} I beseech 
thee, O Father of compassion, vouchsafe to 
forgive the souls of 
the faithful departed 
whereinsoever they 
have sinned against 
thee by any one of 
the seven mortal sins, 
and especially wherein they have not forgiven those who had 
trespassed against 
them, or have not 
loved their enemies. 
And for all these their 
sins I offer thee that 
most sweet and tender 
prayer which thy Son 
prayed to thee for his 
enemies while hanging on the cross. Amen. 

\emph{And lead us not into 
temptation.} I beseech thee, O Father 
of compassion, vouchsafe to forgive the 
souls of the faithful 
departed whereinsoever they have not resisted their concupiscence and the sins to 
which they were especially prone, but have 
again and again consented to the devil 
and the flesh, and entangled themselves by 
their own will in many 
grievous evils. And 
for all these their manifold sins I offer thee 
the glorious victory 
wherewith thy Son 
overcame the world 
and the devil, together with all his most 
holy life and conversation, his toil and 
weariness, his most 
bitter Passion and his 
Death. Amen. 

\emph{But deliver us and 
them from every evil} 
and every woe through 
the merits of thy beloved Son, and bring 
us to the kingdom of 
thy glory, which is 
none other than thy 
most glorious self. Amen. 


\section{Prayer to the Faithful Departed.}

O MOST afflicted 
and unrepining 
souls, may Jesus Christ 
have mercy upon you, 
who for you was crucified and died, and 
may he refresh you in 
your sufferings by the 
sprinkling of his precious Blood. I commend you to that exceeding love which 
drew down the Son of 
God from heaven, and 
constrained him to a 
most bitter death on 
earth, that in that 
amazing compassion 
wherewith he entered 
into and took upon 
himself all the afflictions of the afflicted, 
he may have compassion on you. And for 
your full solace and 
refreshment I offer 
you all that filial love 
which the same Jesus 
Christ felt towards the 
Father in his Divinity, and towards Mary 
in his Humanity. 



\section{Prayer in a Burial Ground.}

HAIL, all ye faithful souls of 
Christ; may he give 
you rest, who is himself the one true Rest. 
May Jesus Christ, the 
Son of the living God, 
who for our salvation 
and for that of all 
mankind was born of 
the Immaculate Virgin, and redeemed 
you with his precious 
Blood, bless you, release you from your 
pain, raise you up in 
the day of judgment, 
and place you with 
his holy angels. 


\end{document}
