\latin{Et non intres in judícium cum servo \textbf{tu}o~:~* quia non justificábitur in conspéctu tuo om\textit{nis} \textbf{vi}vens.}\vern{And enter not into judgment with thy servant: for in thy sight no man living shall be justified.}
\latin{Quia persecútus est inimícus ánimam \textbf{me}am~:~* humiliávit in terra vi\textit{tam} \textbf{me}am.}\vern{For the enemy hath persecuted my soul: he hath brought down my life to the earth.}
\latin{Collocávit me in obscúris sicut mórtuos \textbf{sǽ}culi~:~* et anxiátus est super me spíritus meus, in me turbátum est \textit{cor} \textbf{me}um.}\vern{He hath made me to dwell in darkness as those that have been dead of old: And my spirit is in anguish within me: my heart within me is troubled.}
\latin{Memor fui diérum antiquórum,~† meditátus sum in ómnibus opéribus \textbf{tu}is~:~* in factis mánuum tuárum me\textit{di}\textbf{tá}bar.}\vern{I remembered the days of old, I meditated on all thy works: I meditated upon the works of thy hands.}
\latin{Expándi manus meas \textbf{ad} te~:~* ánima mea sicut terra sine a\textit{qua} \textbf{ti}bi.}\vern{I stretched forth my hands to thee: my soul is as earth without water unto thee.}
\latin{Velóciter exáudi me, \textbf{Dó}mine~:~* defécit spíri\textit{tus} \textbf{me}us.}\vern{Hear me speedily, O Lord: my spirit hath fainted away.}
\latin{Non avértas fáciem tuam \textbf{a} me~:~* et símilis ero descendéntibus \textit{in} \textbf{la}cum.}\vern{Turn not away thy face from me, lest I be like unto them that go down into the pit.}
\latin{Audítam fac mihi mane misericórdiam \textbf{tu}am~:~* quia in te \textit{spe}\textbf{rá}vi.}\vern{Cause me to hear thy mercy in the morning; for in thee have I hoped.}
\latin{Notam fac mihi viam, in qua \textbf{ám}bulem~:~* quia ad te levávi áni\textit{mam} \textbf{me}am.}\vern{Make the way known to me, wherein I should walk: for I have lifted up my soul to thee.}
\latin{Eripe me de inimícis meis, Dómine, ad te con\textbf{fú}gi~:~* doce me fácere voluntátem tuam, quia Deus me\textit{us} \textbf{es} tu.}\vern{Deliver me from my enemies, O Lord, to thee have I fled: Teach me to do thy will, for thou art my God.}
\latin{Spíritus tuus bonus dedúcet me in terram \textbf{re}ctam~:~* propter nomen tuum, Dómine, vivificábis me, in æquitá\textit{te} \textbf{tu}a.}\vern{Thy good spirit shall lead me into the right land: For thy name' s sake, O Lord, thou wilt quicken me in thy justice.}
\latin{Edúces de tribulatióne ánimam \textbf{me}am~:~* et in misericórdia tua dispérdes inimí\textit{cos} \textbf{me}os.}\vern{Thou wilt bring my soul out of trouble: And in thy mercy thou wilt destroy my enemies}
\latin{Et perdes omnes, qui tríbulant ánimam \textbf{me}am,~* quóniam ego ser\textit{vus} \textbf{tu}us sum.}\vern{And thou wilt cut off all them that afflict my soul: for I am thy servant.}
\latin{Réquiem æ\textbf{tér}nam~* dona e\textit{is} \textbf{Dó}mine.}\vern{Eternal rest grant unto them, O Lord.}
\latin{Et lux per\textbf{pé}tua~* lúce\textit{at} \textbf{e}is.}\vern{And may perpetual light shine upon them.}
