\latin{Notam fecísti in pópulis virtútem \textbf{tu}am~:~* Redemísti in bráchio tuo pópulum tuum fílios Ja\textit{cob} \textit{et} \textbf{Jo}seph.}\vern{Thou hast made thy power known among the nations: with thy arm thou hast redeemed thy people the children of Jacob and of Joseph.}
\latin{Vidérunt te aquæ, Deus, vidérunt te \textbf{a}quæ~:~* et timuérunt et turbátæ \textit{sunt} \textit{a}\textbf{býs}si.}\vern{The waters saw thee, O God, the waters saw thee: and they were afraid, and the depths were troubled.}
\latin{Multitúdo sónitus a\textbf{quá}rum~:~* vocem de\textit{dérunt} \textbf{nu}bes.}\vern{Great was the noise of the waters: the clouds sent out a sound.}
\latin{Etenim sagíttæ tuæ \textbf{tráns}eunt~:~* vox tonítrui tu\textit{i} \textit{in} \textbf{ro}ta.}\vern{For thy arrows pass: The voice of thy thunder in a wheel.}
\latin{Illuxérunt coruscatiónes tuæ orbi \textbf{ter}ræ~:~* commóta est, et contré\textit{muit} \textbf{ter}ra.}\vern{Thy lightnings enlightened the world: the earth shook and trembled.}
\latin{In mari via tua, et sémitæ tuæ in aquis \textbf{mul}tis~:~* et vestígia tua non \textit{cogno}\textbf{scén}tur.}\vern{Thy way is in the sea, and thy paths in many waters: and thy footsteps shall not be known.}
\latin{Deduxísti sicut oves pópulum \textbf{tu}um,~* in manu Móy\textit{si} \textit{et} \textbf{A}aron.}\vern{Thou hast conducted thy people like sheep, by the hand of Moses and Aaron.}
\latin{Glória Pátri, et \textbf{Fí}lio,~* et Spirí\textit{tui} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}per,~* et in sǽcula sæcu\textit{lórum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
