\latin{Custódi ánimam meam, \textbf{quó}niam \textbf{san}ctus sum~:~* salvum fac servum tuum, Deus meus, spe\textbf{rán}tem \textbf{in} te.}\vern{Preserve my soul, for I am holy: save thy servant, O my God, that trusteth in thee.}
\latin{Miserére mei, Dómine, quóniam ad te clamávi tota die~:~† lætífica ánimam \textbf{ser}vi \textbf{tu}i,~* quóniam ad te, Dómine, ánimam \textbf{me}am le\textbf{vá}vi.}\vern{Have mercy on me, O Lord, for I have cried to thee all the day. Give joy to the soul of thy servant, for to thee, O Lord, I have lifted up my soul.}
\latin{Quóniam tu, Dómine, su\textbf{á}vis et \textbf{mi}tis~:~* et multæ misericórdiæ ómnibus invo\textbf{cán}ti\textbf{bus} te.}\vern{For thou, O Lord, art sweet and mild: and plenteous in mercy to all that call upon thee.}
\latin{Auribus pércipe, Dómine, orati\textbf{ó}nem \textbf{me}am~:~* et inténde voci deprecati\textbf{ó}nis \textbf{me}æ.}\vern{Give ear, O Lord, to my prayer: and attend to the voice of my petition.}
\latin{In die tribulatiónis meæ cla\textbf{má}vi \textbf{ad} te~:~* quia \textbf{ex}au\textbf{dí}sti me.}\vern{I have called upon thee in the day of my trouble: because thou hast heard me.}
\latin{Non est símilis tui in \textbf{di}is, \textbf{Dó}mine~:~* et non est secúndum \textbf{ó}pera \textbf{tu}a.}\vern{There is none among the gods like unto thee, O Lord: and there is none according to thy works.}
\latin{Omnes gentes quascúmque fecísti, vénient, et adorábunt \textbf{co}ram te, \textbf{Dó}mine~:~* et glorificábunt \textbf{no}men \textbf{tu}um.}\vern{All the nations thou hast made shall come and adore before thee, O Lord: and they shall glorify thy name.}
\latin{Quóniam magnus es tu, et fáciens \textbf{mi}ra\textbf{bí}lia~:~* tu es \textbf{De}us \textbf{so}lus.}\vern{For thou art great and dost wonderful things: thou art God alone.}
\latin{Deduc me, Dómine, in via tua,~† et ingrédiar in veri\textbf{tá}te \textbf{tu}a~:~* lætétur cor meum ut tímeat \textbf{no}men \textbf{tu}um.}\vern{Conduct me, O Lord, in thy way, and I will walk in thy truth: let my heart rejoice that it may fear thy name.}
\latin{Confitébor tibi, Dómine, Deus meus, in toto \textbf{cor}de \textbf{me}o,~* et glorificábo nomen tuum \textbf{in} æ\textbf{tér}num.}\vern{I will praise thee, O Lord my God: with my whole heart, and I will glorify thy name for ever:}
\latin{Quia misericórdia tua \textbf{ma}gna est \textbf{su}per me~:~* et eruísti ánimam meam ex inférno in\textbf{fe}ri\textbf{ó}ri.}\vern{For thy mercy is great towards me: and thou hast delivered my soul out of the lower hell.}
\latin{Deus iníqui insurrexérunt super me,~† et synagóga poténtium quæsiérunt \textbf{á}nimam \textbf{me}am~:~* et non proposuérunt te in con\textbf{spé}ctu \textbf{su}o.}\vern{O God, the wicked are risen up against me, and the assembly of the mighty have sought my soul: and they have not set thee before their eyes.}
\latin{Et tu, Dómine, Deus miserátor \textbf{et} mi\textbf{sé}ricors,~* pátiens, et multæ misericórdi\textbf{æ}, et \textbf{ve}rax.}\vern{And thou, O Lord, art a God of compassion, and merciful, patient, and of much mercy, and true.}
\latin{Réspice in me, et miserére mei,~† da impérium tuum \textbf{pú}ero \textbf{tu}o~:~* et salvum fac fílium an\textbf{cíl}læ \textbf{tu}æ.}\vern{O look upon me, and have mercy on me: give thy command to thy servant, and save the son of thy handmaid.}
\latin{Fac mecum signum in bonum,~† ut vídeant qui odérunt me, et \textbf{con}fun\textbf{dán}tur~:~* quóniam tu, Dómine, adjuvísti me, et conso\textbf{lá}tus \textbf{es} me.}\vern{Shew me a token for good: that they who hate me may see, and be confounded, because thou, O Lord, hast helped me and hast comforted me.}
\latin{Glória \textbf{Pá}tri, et \textbf{Fí}lio,~* et Spi\textbf{rí}tui \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}per,~* et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
