\latin{In die tribulatiónis meæ Deum exquisívi,~† mánibus meis nocte contra \textbf{e}\-um~:~* et non \textit{sum} \textit{de}\textbf{cép}\-tus.}\vern{In the day of my trouble I sought God, with my hands lifted up to him in the night, and I was not deceived.}
\latin{Rénuit consolári ánima mea,~† memor fui Dei, et delectátus sum, et exerci\textbf{tá}\-tus sum~:~* et defécit spí\textit{ritus} \textbf{me}\-us.}\vern{My soul refused to be comforted: I remembered God, and was delighted, and was exercised, and my spirit swooned away.}
\latin{Anticipavérunt vigílias óculi \textbf{me}\-i~:~* turbátus sum, et non \textit{sum} \textit{lo}\textbf{cú}\-tus.}\vern{My eyes prevented the watches: I was troubled, and I spoke not.}
\latin{Cogitávi dies an\textbf{tí}\-quos~:~* et annos ætérnos in \textit{mente} \textbf{há}\-bui.}\vern{I thought upon the days of old: and I had in my mind the eternal years.}
\latin{Et meditátus sum nocte cum corde \textbf{me}\-o,~* et exercitábar, et scopébam spí\textit{ritum} \textbf{me}\-um.}\vern{And I meditated in the night with my own heart: and I was exercised and I swept my spirit.}
\latin{Numquid in ætérnum projíciet \textbf{De}\-us~:~* aut non appónet ut complacíti\textit{or} \textit{sit} \textbf{ad}\-huc?}\vern{Will God then cast off for ever? or will he never be more favourable again?}
\latin{Aut in finem misericórdiam suam ab\textbf{scín}\-det,~* a generatióne in gene\textit{rati}\textbf{ó}\-nem?}\vern{Or will he cut off his mercy for ever, from generation to generation?}
\latin{Aut obliviscétur miseréri \textbf{De}\-us~:~* aut continébit in ira sua misericór\textit{dias} \textbf{su}\-as?}\vern{Or will God forget to shew mercy? or will he in his anger shut up his mercies?}
\latin{Et dixi~: Nunc \textbf{cœ}\-pi~:~* hæc mutátio déxte\textit{ræ} \textit{Ex}\textbf{cél}\-si.}\vern{And I said, Now have I begun: this is the change of the right hand of the most High.}
\latin{Memor fui óperum \textbf{Dó}\-mini~:~* quia memor ero ab inítio mirabíli\textit{um} \textit{tu}\textbf{ó}\-rum.}\vern{I remembered the works of the Lord: for I will be mindful of thy wonders from the beginning.}
\latin{Et meditábor in ómnibus opéribus \textbf{tu}\-is~:~* et in adinventiónibus tuis \textit{exer}\textbf{cé}\-bor.}\vern{And I will meditate on all thy works: and will be employed in thy inventions.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}

