\latin{In die tribulatiónis meæ Deum exquisívi,~† mánibus meis nocte \textbf{con}tra \textbf{e}um~:~* et non \textbf{sum} de\textbf{cép}tus.}\vern{In the day of my trouble I sought God, with my hands lifted up to him in the night, and I was not deceived.}
\latin{Rénuit consolári ánima mea,~† memor fui Dei, et delectátus sum, et ex\textbf{er}ci\textbf{tá}tus sum~:~* et defécit \textbf{spí}ritus \textbf{me}us.}\vern{My soul refused to be comforted: I remembered God, and was delighted, and was exercised, and my spirit swooned away.}
\latin{Anticipavérunt vigílias \textbf{ó}culi \textbf{me}i~:~* turbátus sum, et non \textbf{sum} lo\textbf{cú}tus.}\vern{My eyes prevented the watches: I was troubled, and I spoke not.}
\latin{Cogitávi \textbf{di}es an\textbf{tí}quos~:~* et annos ætérnos in \textbf{men}te \textbf{há}bui.}\vern{I thought upon the days of old: and I had in my mind the eternal years.}
\latin{Et meditátus sum nocte cum \textbf{cor}de \textbf{me}o,~* et exercitábar, et scopébam \textbf{spí}ritum \textbf{me}um.}\vern{And I meditated in the night with my own heart: and I was exercised and I swept my spirit.}
\latin{Numquid in ætérnum pro\textbf{jí}ciet \textbf{De}us~:~* aut non appónet ut complacíti\textbf{or} sit \textbf{ad}huc?}\vern{Will God then cast off for ever? or will he never be more favourable again?}
\latin{Aut in finem misericórdiam \textbf{su}am ab\textbf{scín}det,~* a generatióne in gene\textbf{ra}ti\textbf{ó}nem?}\vern{Or will he cut off his mercy for ever, from generation to generation?}
\latin{Aut obliviscétur mise\textbf{ré}ri \textbf{De}us~:~* aut continébit in ira sua miseri\textbf{cór}dias \textbf{su}as?}\vern{Or will God forget to shew mercy? or will he in his anger shut up his mercies?}
\latin{Et \textbf{di}xi~: Nunc \textbf{cœ}pi~:~* hæc mutátio déxte\textbf{ræ} Ex\textbf{cél}si.}\vern{And I said, Now have I begun: this is the change of the right hand of the most High.}
\latin{Memor fui \textbf{ó}perum \textbf{Dó}mini~:~* quia memor ero ab inítio mirabíli\textbf{um} tu\textbf{ó}rum.}\vern{I remembered the works of the Lord: for I will be mindful of thy wonders from the beginning.}
\latin{Et meditábor in ómnibus o\textbf{pé}ribus \textbf{tu}is~:~* et in adinventiónibus tuis \textbf{ex}er\textbf{cé}bor.}\vern{And I will meditate on all thy works: and will be employed in thy inventions.}
\latin{Glória \textbf{Pá}tri, et \textbf{Fí}lio,~* et Spi\textbf{rí}tui \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}per,~* et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}

