\latin{Notam fecísti in pópulis vir\textbf{tú}\-tem \textbf{tu}\-am~:~* Redemísti in bráchio tuo pópulum tuum fílios \textbf{Ja}\-cob et \textbf{Jo}\-seph.}\vern{Thou hast made thy power known among the nations: With thy arm thou hast redeemed thy people the children of Jacob and of Joseph.}
\latin{Vidérunt te aquæ, Deus, vi\textbf{dé}\-runt te \textbf{a}\-quæ~:~* et timuérunt et turbátæ \textbf{sunt} a\textbf{býs}\-si.}\vern{The waters saw thee, O God, the waters saw thee: and they were afraid, and the depths were troubled.}
\latin{Multitúdo sóni\textbf{tus} a\textbf{quá}\-rum~:~* vocem de\textbf{dé}\-runt \textbf{nu}\-bes.}\vern{Great was the noise of the waters: the clouds sent out a sound.}
\latin{Etenim sagíttæ \textbf{tu}æ \textbf{tráns}\-eunt~:~* vox tonítrui \textbf{tu}\-i in \textbf{ro}\-ta.}\vern{For thy arrows pass: The voice of thy thunder in a wheel.}
\latin{Illuxérunt coruscatiónes tuæ \textbf{or}\-bi \textbf{ter}\-ræ~:~* commóta est, et con\textbf{tré}\-muit \textbf{ter}\-ra.}\vern{Thy lightnings enlightened the world: the earth shook and trembled.}
\latin{In mari via tua, et sémitæ tuæ in \textbf{a}\-quis \textbf{mul}\-tis~:~* et vestígia tua non \textbf{co}\-gno\textbf{scén}\-tur.}\vern{Thy way is in the sea, and thy paths in many waters: and thy footsteps shall not be known.}
\latin{Deduxísti sicut oves \textbf{pó}\-pulum \textbf{tu}\-um,~* in manu Móy\textbf{si} et \textbf{A}\-aron.}\vern{Thou hast conducted thy people like sheep, by the hand of Moses and Aaron.}
\latin{Glória \textbf{Pá}\-tri, et \textbf{Fí}\-lio,~* et Spi\textbf{rí}\-tui \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}\-per,~* et in sǽcula sæcu\textbf{ló}\-rum. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
