\latin{Custódi ánimam meam, quóniam \textbf{san}\-ctus sum~:~* salvum fac servum tuum, Deus meus, spe\textit{rántem} \textbf{in} te.}\vern{Preserve my soul, for I am holy: save thy servant, O my God, that trusteth in thee.}
\latin{Miserére mei, Dómine, quóniam ad te clamávi tota die~:~† lætífica ánimam servi \textbf{tu}\-i,~* quóniam ad te, Dómine, ánimam me\textit{am} \textit{le}\textbf{vá}\-vi.}\vern{Have mercy on me, O Lord, for I have cried to thee all the day. Give joy to the soul of thy servant, for to thee, O Lord, I have lifted up my soul.}
\latin{Quóniam tu, Dómine, suávis et \textbf{mi}\-tis~:~* et multæ misericórdiæ ómnibus invo\textit{cánti}\textbf{bus} te.}\vern{For thou, O Lord, art sweet and mild: and plenteous in mercy to all that call upon thee.}
\latin{Auribus pércipe, Dómine, oratiónem \textbf{me}\-am~:~* et inténde voci deprecati\textit{ónis} \textbf{me}æ.}\vern{Give ear, O Lord, to my prayer: and attend to the voice of my petition.}
\latin{In die tribulatiónis meæ clamávi \textbf{ad} te~:~* quia \textit{exau}\textbf{dí}\-sti me.}\vern{I have called upon thee in the day of my trouble: because thou hast heard me.}
\latin{Non est símilis tui in diis, \textbf{Dó}\-mine~:~* et non est secúndum ó\textit{pera} \textbf{tu}\-a.}\vern{There is none among the gods like unto thee, O Lord: and there is none according to thy works.}
\latin{Omnes gentes quascúmque fecísti, vénient, et adorábunt coram te, \textbf{Dó}\-mine~:~* et glorificábunt \textit{nomen} \textbf{tu}\-um.}\vern{All the nations thou hast made shall come and adore before thee, O Lord: and they shall glorify thy name.}
\latin{Quóniam magnus es tu, et fáciens mira\textbf{bí}\-lia~:~* tu es \textit{Deus} \textbf{so}\-lus.}\vern{For thou art great and dost wonderful things: thou art God alone.}
\latin{Deduc me, Dómine, in via tua,~† et ingrédiar in veritáte \textbf{tu}\-a~:~* lætétur cor meum ut tímeat \textit{nomen} \textbf{tu}\-um.}\vern{Conduct me, O Lord, in thy way, and I will walk in thy truth: let my heart rejoice that it may fear thy name.}
\latin{Confitébor tibi, Dómine, Deus meus, in toto corde \textbf{me}\-o,~* et glorificábo nomen tuum \textit{in} \textit{æ}\textbf{tér}\-num.}\vern{ I will praise thee, O Lord my God: with my whole heart, and I will glorify thy name for ever:}
\latin{Quia misericórdia tua magna est \textbf{su}\-per me~:~* et eruísti ánimam meam ex inférno in\textit{feri}\textbf{ó}\-ri.}\vern{For thy mercy is great towards me: and thou hast delivered my soul out of the lower hell.}
\latin{Deus iníqui insurrexérunt super me,~† et synagóga poténtium quæsiérunt ánimam \textbf{me}\-am~:~* et non proposuérunt te in con\textit{spéctu} \textbf{su}\-o.}\vern{O God, the wicked are risen up against me, and the assembly of the mighty have sought my soul: and they have not set thee before their eyes.}
\latin{Et tu, Dómine, Deus miserátor et mi\textbf{sé}\-ricors,~* pátiens, et multæ misericórdi\textit{æ}, \textit{et} \textbf{ve}\-rax.}\vern{And thou, O Lord, art a God of compassion, and merciful, patient, and of much mercy, and true.}
\latin{Réspice in me, et miserére mei,~† da impérium tuum púero \textbf{tu}\-o~:~* et salvum fac fílium an\textit{cíllæ} \textbf{tu}æ.}\vern{O look upon me, and have mercy on me: give thy command to thy servant, and save the son of thy handmaid.}
\latin{Fac mecum signum in bonum,~† ut vídeant qui odérunt me, et confun\textbf{dán}\-tur~:~* quóniam tu, Dómine, adjuvísti me, et conso\textit{látus} \textbf{es} me.}\vern{Shew me a token for good: that they who hate me may see, and be confounded, because thou, O Lord, hast helped me and hast comforted me.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
