\latin{Miserére mei, Dómine, quóniam in\textbf{fír}\-mus sum~:~* sana me, Dómine, quóniam conturbáta sunt \textit{ossa} \textbf{me}\-a.}\vern{Have mercy on me, O Lord, for I am weak: heal me, O Lord, for my bones are troubled.}
\latin{Et ánima mea turbáta est \textbf{val}\-de~:~* sed tu, Dó\textit{mine}, \textbf{ús}\-quequo?}\vern{And my soul is troubled exceedingly: but thou, O Lord, how long?}
\latin{Convértere, Dómine, et éripe ánimam \textbf{me}\-am~:~* salvum me fac propter misericór\textit{diam} \textbf{tu}\-am.}\vern{Turn to me, O Lord, and deliver my soul: O save me for thy mercy' s sake.}
\latin{Quóniam non est in morte qui memor sit \textbf{tu}\-i~:~* in inférno autem quis confité\textit{bitur} \textbf{ti}\-bi?}\vern{For there is no one in death, that is mindful of thee: and who shall confess to thee in hell?}
\latin{Laborávi in gémitu meo,~† lavábo per síngulas noctes lectum \textbf{me}\-um~:~* lácrimis meis stratum me\textit{um} \textit{ri}\-\textbf{gá}\-bo.}\vern{I have laboured in my groanings, every night I will wash my bed: I will water my couch with my tears.}
\latin{Turbátus est a furóre óculus \textbf{me}\-us~:~* inveterávi inter omnes ini\textit{mícos} \textbf{me}\-os.}\vern{My eye is troubled through indignation: I have grown old amongst all my enemies.}
\latin{Discédite a me, omnes, qui operámini iniqui\textbf{tá}\-tem~:~* quóniam exaudívit Dóminus vocem \textit{fletus} \textbf{me}\-i.}\vern{Depart from me, all ye workers of iniquity: for the Lord hath heard the voice of my weeping.}
\latin{Exaudívit Dóminus deprecatiónem \textbf{me}\-am,~* Dóminus oratiónem me\textit{am} \textit{sus}\-\textbf{cé}\-pit.}\vern{The Lord hath heard my supplication: the Lord hath received my prayer.}
\latin{Erubéscant, et conturbéntur veheménter omnes inimíci \textbf{me}\-i~:~* convertántur et erubéscant val\textit{de} \textit{ve}\-\textbf{ló}\-citer.}\vern{Let all my enemies be ashamed, and be very much troubled: let them be turned back, and be ashamed very speedily.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
