%\latin{Justum adjutórium meum a \textbf{Dó}\-mino,~* qui salvos facit \textit{rectos} \textbf{cor}\-de.}\vern{Just is my help from the Lord: who saveth the upright of heart.}
\latin{Deus judex justus, fortis, et \textbf{pá}\-tiens~:~* numquid iráscitur per sín\textit{gulos} \textbf{di}\-es?}\vern{God is a just judge, strong and patient: is he angry every day?}
\latin{Nisi convérsi fuéritis, gládium suum vi\textbf{brá}\-bit~:~* arcum suum teténdit, et pa\textit{rávit} \textbf{il}\-lum.}\vern{Except you will be converted, he will brandish his sword: he hath bent his bow and made it ready.}
\latin{Et in eo parávit vasa \textbf{mor}\-tis~:~* sagíttas suas ardénti\textit{bus} \textit{ef}\-\textbf{fé}\-cit.}\vern{And in it he hath prepared the instruments of death, he hath made ready his arrows for them that burn.}
\latin{Ecce partúriit inju\textbf{stí}\-tiam~:~* concépit dolórem, et péperit in\textit{iqui}\-\textbf{tá}\-tem.}\vern{Behold he hath been in labour with injustice; he hath conceived sorrow, and brought forth iniquity.}
\latin{Lacum apéruit, et effódit \textbf{e}\-um~:~* et íncidit in fóve\textit{am} \textit{quam} \textbf{fe}\-cit.}\vern{He hath opened a pit and dug it; and he is fallen into the hole he made.}
\latin{Convertétur dolor ejus in caput \textbf{e}\-jus~:~* et in vérticem ipsíus iníquitas e\textit{jus} \textit{de}\-\textbf{scén}\-det.}\vern{His sorrow shall be turned on his own head: and his iniquity shall comedown upon his crown.}
\latin{Confitébor Dómino secúndum justítiam \textbf{e}\-jus~:~* et psallam nómini Dómi\textit{ni} \textit{al}\-\textbf{tís}\-simi.}\vern{I will give glory to the Lord according to his justice: and will sing to the name of the Lord the most high.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in sǽcula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
