\latin{Bénedic, ánima mea, \textbf{Dó}\-mino~:~* et noli oblivísci omnes retributi\textbf{ó}\-nes \textbf{e}\-jus.}\vern{Bless the Lord, O my soul, and never forget all he hath done for thee.}
\latin{Qui propitiátur ómnibus iniquitátibus \textbf{tu}\-is~:~* qui sanat omnes infirmi\textbf{tá}\-tes \textbf{tu}\-as.}\vern{Who forgiveth all thy iniquities: who healeth all thy diseases.}
\latin{Qui rédimit de intéritu vitam \textbf{tu}\-am~:~* qui corónat te in misericórdia et mise\textbf{ra}\-ti\textbf{ó}\-nibus.}\vern{Who redeemeth thy life from destruction: who crowneth thee with mercy and compassion.}
\latin{Qui replet in bonis desidérium \textbf{tu}\-um~:~* renovábitur ut áquilæ ju\textbf{vén}\-tus \textbf{tu}\-a.}\vern{Who satisfieth thy desire with good things: thy youth shall be renewed like the eagle's.}
\latin{Fáciens misericórdias \textbf{Dó}\-minus~:~* et judícium ómnibus injúriam \textbf{pa}\-ti\textbf{én}\-tibus.}\vern{The Lord doth mercies, and judgment for all that suffer wrong.}
\latin{Notas fecit vias suas \textbf{Mó}\-ysi,~* fíliis Israël volun\textbf{tá}\-tes \textbf{su}\-as.}\vern{He hath made his ways known to Moses: his wills to the children of Israel.}
\latin{Miserátor, et miséricors \textbf{Dó}\-minus~:~* longánimis et \textbf{mul}\-tum mi\textbf{sé}\-ricors.}\vern{The Lord is compassionate and merciful: longsuffering and plenteous in mercy.}
\latin{Non in perpétuum ira\textbf{scé}\-tur~:~* neque in ætérnum \textbf{com}\-mi\textbf{ná}\-bitur.}\vern{He will not always be angry: nor will he threaten for ever.}
\latin{Non secúndum peccáta nostra fecit \textbf{no}\-bis~:~* neque secúndum iniquitátes nostras re\textbf{trí}\-buit \textbf{no}\-bis.}\vern{He hath not dealt with us according to our sins: nor rewarded us according to our iniquities.}
\latin{Quóniam secúndum altitúdinem cæli a \textbf{ter}\-ra~:~* corroborávit misericórdiam suam \textbf{su}\-per ti\textbf{mén}\-tes se.}\vern{For according to the height of the heaven above the earth: he hath strengthened his mercy towards them that fear him.}
\latin{Quantum distat ortus ab occi\textbf{dén}\-te~:~* longe fecit a nobis iniqui\textbf{tá}\-tes \textbf{no}\-stras.}\vern{As far as the east is from the west, so far hath he removed our iniquities from us.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spi\textbf{rí}\-tui \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textbf{ló}\-rum. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}

