\latin{Dicet Dómino~: Suscéptor meus es tu, et refúgium \textbf{me}\-um~:~* Deus meus sperá\textit{bo} \textit{in} \textbf{e}\-um.}\vern{He shall say to the Lord: Thou art my protector, and my refuge: my God, in him will I trust.}
\latin{Quóniam ipse liberávit me de láqueo ve\textbf{nán}\-tium,~* et a \textit{verbo} \textbf{á}\-spero.}\vern{For he hath delivered me from the snare of the hunters: and from the sharp word.}
\latin{Scápulis suis obumbrábit \textbf{ti}\-bi~:~* et sub pennis e\textit{jus} \textit{spe}\-\textbf{rá}\-bis.}\vern{He will overshadow thee with his shoulders: and under his wings thou shalt trust.}
\latin{Scuto circúmdabit te véritas \textbf{e}\-jus~:~* non timébis a timó\textit{re} \textit{no}\-\textbf{ctúr}\-no.}\vern{His truth shall compass thee with a shield: thou shalt not be afraid of the terror of the night.}
\latin{A sagítta volánte in die,~† a negótio perambulánte in \textbf{té}\-nebris~:~* ab incúrsu et dæmónio me\textit{ridi}\-\textbf{á}\-no.}\vern{Of the arrow that flieth in the day, of the business that walketh about in the dark: of invasion, or of the noonday devil.}
\latin{Cadent a látere tuo mille,~† et decem míllia a dextris \textbf{tu}\-is~:~* ad te autem non ap\textit{propin}\-\textbf{quá}\-bit.}\vern{A thousand shall fall at thy side, and ten thousand at thy right hand: but it shall not come nigh thee.}
\latin{Verúmtamen óculis tuis conside\-\textbf{rá}\-bis~:~* et retributiónem peccató\textit{rum} \textit{vi}\-\textbf{dé}\-bis.}\vern{But thou shalt consider with thy eyes: and shalt see the reward of the wicked.}
\latin{Quóniam tu es, Dómine, spes \textbf{me}\-a~:~* Altíssimum posuísti refú\textit{gium} \textbf{tu}\-um.}\vern{Because thou, O Lord, art my hope: thou hast made the most High thy refuge.}
\latin{Non accédet ad te \textbf{ma}\-lum~:~* et flagéllum non appropinquábit taberná\textit{culo} \textbf{tu}\-o.}\vern{There shall no evil come to thee: nor shall the scourge come near thy dwelling.}
\latin{Quóniam Angelis suis mandávit \textbf{de} te~:~* ut custódiant te in ómnibus \textit{viis} \textbf{tu}\-is.}\vern{For he hath given his angels charge over thee; to keep thee in all thy ways.}
\latin{In mánibus por\textbf{tá}\-bunt te~:~* ne forte offéndas ad lápidem \textit{pedem} \textbf{tu}\-um.}\vern{In their hands they shall bear thee up: lest thou dash thy foot against a stone.}
\latin{Super áspidem et basilíscum ambu\textbf{lá}\-bis~:~* et conculcábis leónem \textit{et} \textit{dra}\-\textbf{có}\-nem.}\vern{Thou shalt walk upon the asp and the basilisk: and thou shalt trample under foot the lion and the dragon.}
\latin{Quóniam in me sperávit, liberábo \textbf{e}\-um~:~* prótegam eum quóniam cognóvit \textit{nomen} \textbf{me}\-um.}\vern{Because he hoped in me I will deliver him: I will protect him because he hath known my name.}
\latin{Clamábit ad me, et ego exáudiam eum~:~† cum ipso sum in tribulati\textbf{ó}\-ne~:~* erípiam eum et glorifi\textit{cábo} \textbf{e}\-um.}\vern{He shall cry to me, and I will hear him: I am with him in tribulation, I will deliver him, and I will glorify him.}
\latin{Longitúdine diérum replébo \textbf{e}\-um~:~* et osténdam illi salu\textit{táre} \textbf{me}\-um.}\vern{I will fill him with length of days; and I will shew him my salvation.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in sǽcula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
