\latin{Miserére \textbf{me}\-i,~* et exáudi orati\textit{ónem} \textbf{me}\-am.}\vern{Have mercy on me: and hear my prayer.}
\latin{Fílii hóminum, úsquequo gravi \textbf{cor}\-de?~* ut quid dilígitis vanitátem et quaéri\textit{tis} \textit{men}\-\textbf{dá}\-cium?}\vern{O ye sons of men, how long will you be dull of heart? why do you love vanity, and seek after lying?}
\latin{Et scitóte quóniam mirificávit Dóminus sanctum \textbf{su}\-um~:~* Dóminus exáudiet me cum clamáve\textit{ro} \textit{ad} \textbf{e}\-um.}\vern{Know ye also that the Lord hath made his holy one wonderful: the Lord will hear me when I shall cry unto him.}
\latin{Irascímini, et nolíte peccáre~:~† quæ dícitis in córdibus \textbf{ve}\-stris,~* in cubílibus vestris \textit{compun}\-\textbf{gí}\-mini.}\vern{Be angry, and sin not: the things you say in your hearts, be sorry for them upon your beds.}
\latin{Sacrificáte sacrifícium justítiæ,~† et speráte in \textbf{Dó}\-mino.~* Multi dicunt~: quis osténdit \textit{nobis} \textbf{bo}\-na?}\vern{Offer up the sacrifice of justice, and trust in the Lord: many say, Who sheweth us good things?}
\latin{Signátum est super nos lumen vultus tui, \textbf{Dó}\-mine~:~* dedísti lætítiam in \textit{corde} \textbf{me}\-o.}\vern{The light of thy countenance O Lord, is signed upon us: thou hast given gladness in my heart.}
\latin{A fructu fruménti, vini et ólei \textbf{su}\-i~* mul\textit{tipli}\-\textbf{cá}\-ti sunt.}\vern{By the fruit of their corn, their wine and oil, they are multiplied.}
\latin{In pace in i\textbf{dí}\-psum~* dórmiam et \textit{requi}\-\textbf{é}\-scam~;}\vern{In peace in the selfsame I will sleep, and I will rest:}
\latin{Quóniam tu, Dómine, singuláriter \textbf{in} spe~* con\textit{stitu}\-\textbf{í}\-sti me.}\vern{For thou, O Lord, singularly hast settled me in hope.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
