%\latin{Confundántur, et defíciant detrahéntes ánimæ \textbf{me}æ~:~* operiántur confusióne et pudóre, qui quærunt \textit{mala} \textbf{mi}\-hi.}\vern{Let them be confounded and come to nothing that detract my soul; let them be covered with confusion and shame that seek my hurt.}
\latin{Ego autem semper spe\textbf{rá}\-bo~:~* et adjíciam super omnem \textit{laudem} \textbf{tu}\-am.}\vern{But I will always hope; and will add to all thy praise.}
\latin{Os meum annuntiábit justítiam \textbf{tu}\-am~:~* tota die salu\textit{táre} \textbf{tu}\-um.}\vern{My mouth shall shew forth thy justice; thy salvation all the day long.}
\latin{Quóniam non cognóvi litteratúram,~† introíbo in poténtias \textbf{Dó}\-mi\-ni~:~* Dómine, memorábor justítiæ tu\textit{æ} \textit{so}\-\textbf{lí}\-us.}\vern{Because I have not known learning, I will enter into the powers of the Lord: O Lord, I will be mindful of thy justice alone.}
\latin{Deus, docuísti me a juventúte \textbf{me}\-a~:~* et usque nunc pronuntiábo mirabí\textit{lia} \textbf{tu}\-a.}\vern{Thou hast taught me, O God, from my youth: and till now I will declare thy wonderful works.}
\latin{Et usque in senéctam et \textbf{sé}\-nium~:~* Deus, ne \textit{dere}\-\textbf{lín}\-quas me,}\vern{And unto old age and grey hairs: O God, forsake me not,}
\latin{Donec annúntiem bráchium \textbf{tu}\-um~* generatióni omni, \textit{quæ} \textit{ven}\-\textbf{tú}\-ra est~:}\vern{Until I shew forth thy arm to all the generation that is to come:}
\latin{Poténtiam tuam, et justítiam tuam, Deus,~† usque in altíssima, quæ fecísti ma\textbf{gná}\-lia~:~* Deus, quis sí\textit{milis} \textbf{ti}\-bi?}\vern{Thy power, And thy justice, O God, even to the highest great things thou hast done: O God, who is like to thee?}
\latin{Quantas ostendísti mihi tribulatiónes multas et malas~:~† et convérsus vivifi\textbf{cá}\-sti me~:~* et de abýssis terræ íterum \textit{redu}\-\textbf{xí}\-sti me~:}\vern{How great troubles hast thou shewn me, many and grievous: and turning thou hast brought me to life, and hast brought me back again from the depths of the earth:}
\latin{Multiplicásti magnificéntiam \textbf{tu}\-am~:~* et convérsus conso\textit{látus} \textbf{es} me.}\vern{Thou hast multiplied thy magnificence; and turning to me thou hast comforted me.}
\latin{Nam et ego confitébor tibi in vasis psalmi veritátem \textbf{tu}\-am~:~* Deus, psallam tibi in cíthara, \textit{Sanctus} \textbf{Is}\-raël.}\vern{For I will also confess to thee thy truth with the instruments of psaltery: O God, I will sing to thee with the harp, thou holy one of Israel.}
\latin{Exsultábunt lábia mea cum cantávero \textbf{ti}\-bi~:~* et ánima mea, quam \textit{rede}\-\textbf{mí}\-sti.}\vern{My lips shall greatly rejoice, when I shall sing to thee; and my soul which thou hast redeemed.}
\latin{Sed et lingua mea tota die meditábitur justítiam \textbf{tu}\-am~:~* cum confúsi et revériti fúerint, qui quærunt \textit{mala} \textbf{mi}\-hi.}\vern{Yea and my tongue shall meditate on thy justice all the day; when they shall be confounded and put to shame that seek evils to me.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tui} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in sǽcula sæcu\textit{lórum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
