\latin{Vana locúti sunt unusquísque ad próximum \textbf{su}um~:~* lábia dolósa, in corde et cor\textit{de} \textit{lo}\-\textbf{cú}ti sunt.}\vern{They have spoken vain things every one to his neighbour: with deceitful lips, and with a double heart have they spoken.}
\latin{Dispérdat Dóminus univérsa lábia do\textbf{ló}sa,~* et lin\textit{guam} \textit{ma}\-\textbf{gní}loquam.}\vern{May the Lord destroy all deceitful lips, and the tongue that speaketh proud things.}
\latin{Qui dixérunt~: Linguam nostram magnificábimus,~† lábia nostra a \textbf{no}bis sunt,~* quis noster \textit{Dó}\-\textit{mi}\-\textbf{nus} est?}\vern{Who have said: We will magnify our tongue; our lips are our own; who is Lord over us?}
\latin{Propter misériam ínopum, et gémitum \textbf{páu}perum,~* nunc exsúrgam, \textit{di}\-\textit{cit} \textbf{Dó}minus.}\vern{By reason of the misery of the needy, and the groans of the poor, now will I arise, saith the Lord.}
\latin{Ponam in salu\textbf{tá}ri~:~* fiduciáliter a\textit{gam} \textit{in} \textbf{e}o.}\vern{I will set him in safety; I will deal confidently in his regard.}
\latin{Elóquia Dómini, elóquia \textbf{ca}sta~:~* argéntum igne examinátum, probátum terræ pur\textit{gá}\-\textit{tum} \textbf{sép}tuplum.}\vern{The words of the Lord are pure words: as silver tried by the fire, purged from the earth refined seven times.}
\latin{Tu, Dómine, servábis nos~: et custódi\textbf{es} nos~* a generatióne hac \textit{in} \textit{æ}\-\textbf{tér}num.}\vern{Thou, O Lord, wilt preserve us: and keep us from this generation for ever.}
\latin{In circúitu ímpii \textbf{ám}bulant~:~* secúndum altitúdinem tuam multiplicásti fí\textit{li}\-\textit{os} \textbf{hó}minum.}\vern{The wicked walk round about: according to thy highness, thou hast multiplied the children of men.}
\latin{Glória Pátri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\-\textit{i} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}per,~* et in sǽcula sæcu\textit{ló}\-\textit{rum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
