\latin{Quámdiu ponam consília in ánima \textbf{me}\-a,~* dolórem in corde me\textit{o} \textit{per} \textbf{di}\-em?}\vern{How long shall I take counsels in my soul, sorrow in my heart all the day?}
\latin{Usquequo exaltábitur inimícus meus \textbf{su}\-per me?~* réspice, et exáudi me, Dómine, \textit{De}\-\textit{us} \textbf{me}\-us.}\vern{How long shall my enemy be exalted over me? Consider, and hear me, O Lord my God.}
\latin{Illúmina óculos meos ne umquam obdórmiam in \textbf{mor}\-te~:~* nequándo dicat inimícus meus~: præválui ad\textit{vér}\-\textit{sus} \textbf{e}\-um.}\vern{Enlighten my eyes that I never sleep in death: Lest at any time my enemy say: I have prevailed against him.}
\latin{Qui tríbulant me, exsultábunt si motus \textbf{fú}\-ero~:~* ego autem in misericórdia tu\textit{a} \textit{spe}\-\textbf{rá}\-vi.}\vern{They that trouble me will rejoice when I am moved: But I have trusted in thy mercy.}
\latin{Exsultábit cor meum in salutári tuo~:~† cantábo Dómino qui bona tríbuit \textbf{mi}\-hi~:~* et psallam nómini Dómi\textit{ni} \textit{al}\-\textbf{tís}\-simi.}\vern{My heart shall rejoice in thy salvation: I will sing to the Lord, who giveth me good things: yea I will sing to the name of the Lord the most high.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tu}\-\textit{i} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textit{ló}\-\textit{rum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
