\latin{Sanctis, qui sunt in terra \textbf{e}\-jus,~* mirificávit omnes voluntátes me\textit{as} \textit{in} \textbf{e}\-is.}\vern{To the saints, who are in his land, he hath made wonderful all my desires in them.}
\latin{Multiplicátæ sunt infirmitátes e\-\textbf{ó}\-rum~:~* póstea acce\textit{le}\-\textit{ra}\-\textbf{vé}\-runt.}\vern{Their infirmities were multiplied: afterwards they made haste.}
\latin{Non congregábo conventícula eórum de san\textbf{guí}\-nibus,~* nec memor ero nóminum eórum per lá\textit{bi}\-\textit{a} \textbf{me}\-a.}\vern{I will not gather together their meetings for blood offerings: nor will I be mindful of their names by my lips.}
\latin{Dóminus pars hereditátis meæ, et cálicis \textbf{me}\-i~:~* tu es, qui restítues hereditátem \textit{me}\-\textit{am} \textbf{mi}\-hi.}\vern{The Lord is the portion of my inheritance and of my cup: it is thou that wilt restore my inheritance to me.}
\latin{Funes cecidérunt mihi in præ\textbf{clá}\-ris~:~* étenim heréditas mea præclá\textit{ra} \textit{est} \textbf{mi}\-hi.}\vern{The lines are fallen unto me in goodly places: for my inheritance is goodly to me.}
\latin{Benedícam Dóminum, qui tríbuit mihi intel\textbf{lé}\-ctum~:~* ínsuper et usque ad noctem increpuérunt me \textit{re}\-\textit{nes} \textbf{me}\-i.}\vern{I will bless the Lord, who hath given me understanding: moreover my reins also have corrected me even till night}
\latin{Providébam Dóminum in conspéctu meo \textbf{sem}\-per~:~* quóniam a dextris est mihi, \textit{ne} \textit{com}\-\textbf{mó}\-vear.}\vern{I set the Lord always in my sight: for he is at my right hand, that I be not moved.}
\latin{Propter hoc lætátum est cor meum, et exsultávit lingua \textbf{me}\-a~:~* ínsuper et caro mea requi\textit{é}\-\textit{scet} \textbf{in} spe.}\vern{Therefore my heart hath been glad, and my tongue hath rejoiced: moreover my flesh also shall rest in hope.}
\latin{Quóniam non derelínques ánimam meam in in\textbf{fér}\-no~:~* nec dabis sanctum tuum vidére cor\textit{rup}\-\textit{ti}\-\textbf{ó}\-nem.}\vern{Because thou wilt not leave my soul in hell; nor wilt then give thy holy one to see corruption.}
\latin{Notas mihi fecísti vias vitæ,~† adimplébis me lætítia cum vultu \textbf{tu}\-o~:~* delectatiónes in déxtera tua us\textit{que} \textit{in} \textbf{fi}\-nem.}\vern{Thou hast made known to me the ways of life, thou shalt fill me with joy with thy countenance: at thy right hand are delights even to the end.}
\latin{Glória Pátri, et \textbf{Fí}\-lio,~* et Spirí\textit{tu}\-\textit{i} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}\-per,~* et in saécula sæcu\textit{ló}\-\textit{rum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
