\latin{Quis est homo \textbf{qui} vult \textbf{vi}tam~:~* díligit dies vidé\textit{re} \textbf{bo}nos?}\vern{Who is the man that desireth life: who loveth to see good days?}
\latin{Próhibe linguam \textbf{tu}am a \textbf{ma}lo~:~* et lábia tua ne loquán\textit{tur} \textbf{do}lum.}\vern{Keep thy tongue from evil, and thy lips from speaking guile.}
\latin{Divérte a malo, \textbf{et} fac \textbf{bo}num~:~* inquíre pacem, et perséque\textit{re} \textbf{e}am.}\vern{Turn away from evil and do good: seek after peace and pursue it.}
\latin{Oculi Dómini \textbf{su}per \textbf{ju}stos~:~* et aures ejus in preces \textit{e}\-\textbf{ó}rum.}\vern{The eyes of the Lord are upon the just: and his ears unto their prayers.}
\latin{Vultus autem Dómini super faci\textbf{én}tes \textbf{ma}la~:~* ut perdat de terra memóriam \textit{e}\-\textbf{ó}rum.}\vern{But the countenance of the Lord is against them that do evil things: to cut off the remembrance of them from the earth.}
\latin{Clamavérunt justi, et Dóminus exau\textbf{dí}vit \textbf{e}os~:~* et ex ómnibus tribulatiónibus eórum liberá\textit{vit} \textbf{e}os.}\vern{The just cried, and the Lord heard them: and delivered them out of all their troubles.}
\latin{Juxta est Dóminus iis, qui tribu\textbf{lá}to sunt \textbf{cor}de~:~* et húmiles spíritu \textit{sal}\-\textbf{vá}bit.}\vern{The Lord is nigh unto them that are of a contrite heart: and he will save the humble of spirit.}
\latin{Multæ tribulati\textbf{ó}nes ju\textbf{stó}rum~:~* et de ómnibus his liberábit e\textit{os} \textbf{Dó}minus.}\vern{Many are the afflictions of the just; but out of them all will the Lord deliver them.}
\latin{Custódit Dóminus ómnia \textbf{os}sa e\textbf{ó}rum~:~* unum ex his non con\textit{te}\-\textbf{ré}tur.}\vern{The Lord keepeth all their bones, not one of them shall be broken.}
\latin{Mors pecca\textbf{tó}rum \textbf{pés}\-\textbf{si}ma~:~* et qui odérunt justum, \textit{de}\-\textbf{lín}quent.}\vern{The death of the wicked is very evil: and they that hate the just shall be guilty.}
\latin{Rédimet Dóminus ánimas ser\textbf{vó}rum su\textbf{ó}rum~:~* et non delínquent omnes qui sperant \textit{in} \textbf{e}o.}\vern{The Lord will redeem the souls of his servants: and none of them that trust in him shall offend.}
\latin{Glória \textbf{Pá}tri, et \textbf{Fí}\-\textbf{li}o,~* et Spirítu\textit{i} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
