\latin{A fínibus terræ ad \textbf{te} cla\textbf{má}\-vi~:~* dum anxiarétur cor meum, in petra ex\textit{al}\-\textbf{tá}\-sti me.}\vern{To thee have I cried from the ends of the earth: when my heart was in anguish, thou hast exalted me on a rock.}
\latin{Deduxísti me, quia factus \textbf{es} spes \textbf{me}\-a~:~* turris fortitúdinis a fácie in\textit{i}\-\textbf{mí}\-ci.}\vern{Thou hast conducted me; For thou hast been my hope; a tower of strength against the face of the enemy.}
\latin{Inhabitábo in tabernáculo \textbf{tu}\-o in \textbf{saécu}\-la~:~* prótegar in velaménto alárum \textit{tu}\-\textbf{á}\-rum.}\vern{In thy tabernacle I shall dwell for ever: I shall be protected under the covert of thy wings.}
\latin{Quóniam tu, Deus meus, exaudísti orati\textbf{ó}\-nem \textbf{me}\-am~:~* dedísti hereditátem timéntibus no\textit{men} \textbf{tu}\-um.}\vern{For thou, my God, hast heard my prayer: thou hast given an inheritance to them that fear thy name.}
\latin{Dies super dies \textbf{re}\-gis ad\textbf{jíci}\-es~:~* annos ejus usque in diem generatiónis et genera\textit{ti}\-\textbf{ó}\-nis.}\vern{Thou wilt add days to the days of the king: his years even to generation and generation.}
\latin{Pérmanet in ætérnum in con\textbf{spé}\-ctu \textbf{De}\-i~:~* misericórdiam et veritátem ejus quis \textit{re}\-\textbf{quí}\-ret?}\vern{He abideth for ever in the sight of God: his mercy and truth who shall search?}
\latin{Sic psalmum dicam nómini tuo in \textbf{saé}\-culum \textbf{saécu}\-li~:~* ut reddam vota mea de die \textit{in} \textbf{di}\-em.}\vern{So will I sing a psalm to thy name for ever and ever: that I may pay my vows from day to day.}
\latin{Glória \textbf{Pá}\-tri, et \textbf{Fíli}\-o,~* et Spirítu\textit{i} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}\-per,~* et in saécula sæculó\textit{rum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
