\latin{In Dómino laudábitur \textbf{á}\-nima \textbf{me}\-a~:~* áudiant mansuéti, et \textit{læ}\-\textbf{tén}\-tur.}\vern{In the Lord shall my soul be praised: let the meek hear and rejoice.}
\latin{Magnificáte \textbf{Dó}\-minum \textbf{me}\-cum~:~* et exaltémus nomen ejus in \textit{i}\-\textbf{dí}\-psum.}\vern{O magnify the Lord with me; and let us extol his name together.}
\latin{Exquisívi Dóminum, et \textbf{ex}\-au\textbf{dí}\-\textbf{vit} me~:~* et ex ómnibus tribulatiónibus meis erí\textit{pu}\-\textbf{it} me.}\vern{I sought the Lord, and he heard me; and he delivered me from all my troubles.}
\latin{Accédite ad eum, et il\textbf{lu}\-mi\textbf{ná}\-\textbf{mi}\-ni~:~* et fácies vestræ non con\textit{fun}\-\textbf{dén}\-tur.}\vern{Come ye to him and be enlightened: and your faces shall not be confounded.}
\latin{Iste pauper clamávit, et Dóminus exau\textbf{dí}\-vit \textbf{e}\-um~:~* et de ómnibus tribulatiónibus ejus salvá\textit{vit} \textbf{e}\-um.}\vern{This poor man cried, and the Lord heard him: and saved him out of all his troubles.}
\latin{Immíttet Angelus Dómini in circúitu ti\textbf{mén}\-tium \textbf{e}\-um~:~* et erípi\textit{et} \textbf{e}\-os.}\vern{The angel of the Lord shall encamp round about them that fear him: and shall deliver them.}
\latin{Gustáte, et vidéte quóniam su\textbf{á}\-vis est \textbf{Dó}\-\textbf{mi}\-nus~:~* beátus vir, qui sperat \textit{in} \textbf{e}\-o.}\vern{O taste, and see that the Lord is sweet: blessed is the man that hopeth in him.}
\latin{Timéte Dóminum, omnes \textbf{san}\-cti \textbf{e}\-jus~:~* quóniam non est inópia timénti\textit{bus} \textbf{e}\-um.}\vern{Fear the Lord, all ye his saints: for there is no want to them that fear him.}
\latin{Dívites eguérunt et e\textbf{su}\-ri\textbf{é}\-runt~:~* inquiréntes autem Dóminum non minuéntur om\textit{ni} \textbf{bo}\-no.}\vern{The rich have wanted, and have suffered hunger: but they that seek the Lord shall not be deprived of any good.}
\latin{Glória \textbf{Pá}\-tri, et \textbf{Fí}\-\textbf{li}\-o,~* et Spirítu\textit{i} \textbf{Sán}\-cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textbf{núnc}, et \textbf{sém}\-per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}\-men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}

