\latin{Quis est homo qui vult \textbf{vi}tam~:~* díligit dies vi\textit{dé}\textit{re} \textbf{bo}nos?}\vern{Who is the man that desireth life: who loveth to see good days?}
\latin{Próhibe linguam tuam a \textbf{ma}lo~:~* et lábia tua ne lo\textit{quán}\textit{tur} \textbf{do}lum.}\vern{Keep thy tongue from evil, and thy lips from speaking guile.}
\latin{Divérte a malo, et fac \textbf{bo}num~:~* inquíre pacem, et persé\textit{que}\textit{re} \textbf{e}am.}\vern{Turn away from evil and do good: seek after peace and pursue it.}
\latin{Oculi Dómini super \textbf{ju}stos~:~* et aures ejus in pre\textit{ces} \textit{e}\textbf{ó}rum.}\vern{The eyes of the Lord are upon the just: and his ears unto their prayers.}
\latin{Vultus autem Dómini super faciéntes \textbf{ma}la~:~* ut perdat de terra memóri\textit{am} \textit{e}\textbf{ó}rum.}\vern{But the countenance of the Lord is against them that do evil things: to cut off the remembrance of them from the earth.}
\latin{Clamavérunt justi, et Dóminus exaudívit \textbf{e}os~:~* et ex ómnibus tribulatiónibus eórum libe\textit{rá}\textit{vit} \textbf{e}os.}\vern{The just cried, and the Lord heard them: and delivered them out of all their troubles.}
\latin{Juxta est Dóminus iis, qui tribuláto sunt \textbf{cor}de~:~* et húmiles spíri\textit{tu} \textit{sal}\textbf{vá}bit.}\vern{The Lord is nigh unto them that are of a contrite heart: and he will save the humble of spirit.}
\latin{Multæ tribulatiónes ju\textbf{stó}rum~:~* et de ómnibus his liberábit \textit{e}\textit{os} \textbf{Dó}minus.}\vern{Many are the afflictions of the just; but out of them all will the Lord deliver them.}
\latin{Custódit Dóminus ómnia ossa e\textbf{ó}rum~:~* unum ex his non \textit{con}\textit{te}\textbf{ré}tur.}\vern{The Lord keepeth all their bones, not one of them shall be broken.}
\latin{Mors peccatórum \textbf{pés}sima~:~* et qui odérunt ju\textit{stum}, \textit{de}\textbf{lín}quent.}\vern{The death of the wicked is very evil: and they that hate the just shall be guilty.}
\latin{Rédimet Dóminus ánimas servórum su\textbf{ó}rum~:~* et non delínquent omnes qui spe\textit{rant} \textit{in} \textbf{e}o.}\vern{The Lord will redeem the souls of his servants: and none of them that trust in him shall offend.}
\latin{Glória Pátri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
