\latin{A fínibus terræ ad te cla\textbf{má}vi~:~* dum anxiarétur cor meum, in petra \textit{ex}\textit{al}\textbf{tá}sti me.}\vern{To thee have I cried from the ends of the earth: when my heart was in anguish, thou hast exalted me on a rock.}
\latin{Deduxísti me, quia factus es spes \textbf{me}a~:~* turris fortitúdinis a fácie \textit{in}\textit{i}\textbf{mí}ci.}\vern{Thou hast conducted me; For thou hast been my hope; a tower of strength against the face of the enemy.}
\latin{Inhabitábo in tabernáculo tuo in \textbf{sǽ}cula~:~* prótegar in velaménto alá\textit{rum} \textit{tu}\textbf{á}rum.}\vern{In thy tabernacle I shall dwell for ever: I shall be protected under the covert of thy wings.}
\latin{Quóniam tu, Deus meus, exaudísti oratiónem \textbf{me}am~:~* dedísti hereditátem timéntibus \textit{no}\textit{men} \textbf{tu}um.}\vern{For thou, my God, hast heard my prayer: thou hast given an inheritance to them that fear thy name.}
\latin{Dies super dies regis ad\textbf{jí}cies~:~* annos ejus usque in diem generatiónis et gene\textit{ra}\textit{ti}\textbf{ó}nis.}\vern{Thou wilt add days to the days of the king: his years even to generation and generation.}
\latin{Pérmanet in ætérnum in conspéctu \textbf{De}i~:~* misericórdiam et veritátem ejus \textit{quis} \textit{re}\textbf{quí}ret?}\vern{He abideth for ever in the sight of God: his mercy and truth who shall search?}
\latin{Sic psalmum dicam nómini tuo in sǽculum \textbf{sǽ}culi~:~* ut reddam vota mea de di\textit{e} \textit{in} \textbf{di}em.}\vern{So will I sing a psalm to thy name for ever and ever: that I may pay my vows from day to day.}
\latin{Glória Pátri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et núnc, et \textbf{sém}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end. Amen.}
